Fast, Scalable Phrase-Based SMT Decoding

### 2016-02-04 acl.2016/acl2016.tex
acl paper

We trained a phrase-based system using the Moses toolkit with standard settings. The training data consisted of most of the publicly available Arabic-English data from Opus (Jörg Tiedemann, 2012,) containing over 69 million parallel sentences, and tuned on a held out set. The phrase-table was then pruned, keeping only the top 100 entries per source phrase, according to $p(t|s)$. All models files were then binarized; the language models were binaized using KenLM (???), the phrase table using Probing PT (???), lexicalized reordering model using the compact datastructure described in ???. These binary formats were choosen for their best-in-class multithreaded performance. Table~\ref{tab:model-files} gives details of the resultant sizes of the model files. For verification with a different dataset, we also occasionally used a second system trained on the French-English Europarl corpus (2m parallel sentences). 
\begin{table}[h]
\begin{center}
\begin{tabular}{|l|c|c|} \hline
		& ar-en	& fr-en \\ \hline
Phrase table  	& 17 	& 5.8 \\
Language model 	& 3.1  	& 1.8 \\ 
Lex-re model	& 2.3	& 637MB \\ \hline
\end{tabular}
\end{center}
\caption{Model sizes in GB}
\label{tab:model-files}
\end{table}
For testing decoding speed, we used a subset of the training data, Table~\ref{tab:test-sets}. The two test scenarios have differing characterics that we are interested in analyzing, ar-en have short sentences with large models while fr-en have overly long sentences with smaller models.

\begin{table}[h]
\begin{center}
\begin{tabular}{|l|c|c|} \hline
		& ar-en	& fr-en \\ \hline
\# sentences  	& 800k 	& 200k \\
\# words 	& 5.8m 	& 5.9m \\ 
Avg words/sent	& 7.3	& 29.7 \\ \hline
\end{tabular}
\end{center}
\caption{Test sets}
\label{tab:test-sets}
\end{table}

Where we need to compare model scores, we used held out test sets; a 2,000 sentence subset of OpenSubtitles for ar-en and the 3,003 sentence newstest2011 test set for fr-en.

>>>>

We trained a phrase-based system using the Moses toolkit with standard settings. The training data consisted of most of the publicly available Arabic-English data from Opus (Jörg Tiedemann, 2012,) containing over 69 million parallel sentences, and tuned on a held out set. The phrase-table was then pruned, keeping only the top 100 entries per source phrase, according to $p(t|s)$. All models files were then binarized; the language models were binaized using KenLM (???), the phrase table using Probing PT (???), lexicalized reordering model using the compact datastructure described in ???. These binary formats were choosen for their best-in-class multithreaded performance. Table~\ref{tab:model-files} gives details of the resultant sizes of the model files. For verification with a different dataset, we also occasionally used a second system trained on the French-English Europarl corpus (2m parallel sentences). 
\begin{table}[h]
\begin{center}
\begin{tabular}{|l|c|c|} \hline
		& ar-en	& fr-en \\ \hline
Phrase table  	& 17 	& 5.8 \\
Language model 	& 3.1  	& 1.8 \\ 
Lex-re model	& 2.3	& 637MB \\ \hline
\end{tabular}
\end{center}
\caption{Model sizes in GB}
\label{tab:model-files}
\end{table}
For testing decoding speed, we used a subset of the training data, Table~\ref{tab:test-sets}. The two test scenarios have differing characterics that we are interested in analyzing, ar-en have short sentences with large models while fr-en have overly long sentences with smaller models. Where we need to compare model scores, we used held out test sets.

\begin{table}[h]
\begin{center}
\begin{tabular}{|l|r|r|} \hline
		& ar-en		& fr-en \\ \hline
\multicolumn{3}{|l|}{For speed testing} \\ \hline
\# sentences  	& 800k 		& 200k \\
\# words 	& 5.8m 		& 5.9m \\ 
Avg words/sent	& 7.3		& 29.7 \\ \hline
\multicolumn{3}{|l|}{For model score testing} \\ \hline
Set name	& OpenSubtitles	& newstest2011 \\
\# sentences  	& 2000 		& 3003 \\
\# words 	& 14,620 	& 86,162 \\ 
Avg words/sent	& 7.3		& 28.7 \\ \hline
\end{tabular}
\end{center}
\caption{Test sets}
\label{tab:test-sets}
\end{table}
